% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Timo J. Sand}           % name for signature
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left


\begin{letter}{%Ms. Terri Roberts \\
% Senior Staff Recruiter \\
% XYZ Corporation \\
% Rt. 56 \\
% Anytown, New Jersey 05867
}


\begin{flushleft}
{\large\bf Timo J. Sand}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill Korppaanmäentie 2 C 43, 00300, Helsinki \\
\hfill +358 44 565 5606, timo.sand@iki.fi
\end{flushright}
\vfill % forces letterhead to top of page


\opening{Dear Hiring Manager:}

\noindent
% PARAGRAPH ONE: State reason for letter, name the position or type
% of work you are applying for and identify source from  which  you
% learned   of   the  opening.  (i.e.  Career  Development  Center,
% newspaper, employment service, personal contact).
I am writing to apply for the position of Full-Stack Web Developer. I am an undergraduate student at the University of Helsinki Computer Science department and a Senior Software Designer at Steeri Oy. I expect to complete my BSc degree in the summer of 2014 and I will continue studying for my MSc after that. This would likely mean working only part-time during semester. I was made aware of the opening by a message from Panu Ervamaa at http://careers.stackoverflow.com.

\noindent
% PARAGRAPH  TWO:  Indicate why you are interested in the position,
% the company, its products, services - above all, stress what  you
% can  do  for  the employer. If you are a recent graduate, explain
% how your academic background makes you a qualified candidate  for
% the  position.  If  you have practical work experience, point out
% specific achievements or unique qualifications. Try not to repeat
% the  same  information  the reader will find in the resume. Refer
% the reader to the enclosed resume or application which summarizes
% your  qualifications,  training,  and experiences. The purpose of
% this section is to strengthen your resume  by  providing  details
% which bring your experiences to life.

I have always been passionate about web development and have always wanted to do it professionally. I have been involved in web development as a hobby since 2006. One of my strengths lies in being able to handle backend and frontend development simultaneously and thus I would love the opportunity to work as a Full-Stack Web Developer. I have always been pedantic about how to do websites right and I am a strong advocate for a positive and simple UX. I am currently fascinated with JavaScript for full-stack web development, which is why I have been learning NodeJS and AngularJS. Recently I completed a collaborative project with SailsJS for a NodeJS course at the university.
Java has been my primary programming language at work for the past four years and I have been passionately learning Ruby for three years, during which I have been involved in multiple Ruby on Rails projects. Further information about my technological experience can be found in the attached resume.

\noindent
% PARAGRAPH THREE: Request a personal interview and  indicate  your
% flexibility as to the time and place. Repeat your phone number in
% the letter and offer assistance to help in a speedy response. For
% example,  state that you will be in the city where the company is
% located on a certain date and would like to set up an  interview.
% Or,  state  that  you  will  call  on a certain date to set up an
% interview. End the letter by thanking  the  employer  for  taking
% time to consider your credentials.

Frantic has an impressive list of clients and the showcase products look professional and well-made. I have always wanted to be involved in really large web development projects and would love to be part of building great web applications that satisfy customers and the users of these applications.

Attached you will find my curriculum vitae.
Please contact me if you need any further information.
Thank you for your consideration.


\closing{Sincerely yours,}



\encl{}  				% Enclosures

\end{letter}


\end{document}






